Understanding the Lomb-Scargle Periodogram\\ {\it (Draft Version \today)}

### 2017-03-21 PracticalLombScargle.tex
Add acknowledgment

\acknowledgments
{\it Acknowledgments:} I am grateful to Jeff Scargle, Max Mahlke,
and Zeljko Ivezic for helpful feedback on early drafts
of this paper.
This work was supported by the University of Washington eScience Institute,
with funding from the Gordon and Betty Moore Foundation, the Alfred P. Sloan
Foundation, and the Washington Research Foundation.

>>>>

\acknowledgments
{\it Acknowledgments:} I am grateful to Jeff Scargle, Max Mahlke, Dan
Foreman-Mackey, and Zeljko Ivezic for helpful feedback
on early drafts of this paper.
This work was supported by the University of Washington eScience Institute,
with funding from the Gordon and Betty Moore Foundation, the Alfred P. Sloan
Foundation, and the Washington Research Foundation.
